---
title: "Module 5"
author: "Patricia McGee"
date: "2/12/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Module 5 Assignment

The focus of this assignment is learn about Matrix in R. 
For more detail how to work with Matrix in R, click here  Download herefor the worksheet in Matrix.
Plus a more detail on what is inverse Matrix, click here  Download here.  Download .This reference was created by Engineering Mathematics first aid kit published by Pearson Education.  
The R code for inverse Matrix: solve(A). This code is the Inverse of A where A is a square matrix. For complete list of Matrix Algebra in R, visit  Dr. Kabacoff, Quick-R at https://www.statmethods.net/advstats/matrix.html (Links to an external site.)

Your Assignment:
Find the value of inverse of a matrix, determinant of a matrix by using the following values:
A=matrix(1:100, nrow=10)
B=matrix(1:1000, nrow=10)
Post your result and procedure you took on your blog.
A good start will be:
>A <- matrix(1:100, nrow=10)  
>B <- matrix(1:1000, nrow=10)


Reading 

Norman Matloff, The Art of R programming pp. 189-205.



```{r Data, echo=TRUE}




```

## Plots

Here we are creating a side by side boxplot and a histogram

```{r plots, echo=TRUE}
boxplot(Freq, First, Second, FinalDecision, data = patients, names = c("Freq", "First", "Second", "FinalDecision"))

#BP is on a different scale from the other values, so here that is as a separate boxplot
boxplot(BP, data = patients, xlab = "BP")

hist(Freq, data = patients)
hist(BP, data = patients, xlim = range(BP))
hist(First, data = patients)
hist(Second, data = patients)
hist(FinalDecision, data = patients)


```

