---
title: "Module 5"
author: "Patricia McGee"
date: "2/12/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Module 5 Assignment

The focus of this assignment is learn about Matrix in R. 
For more detail how to work with Matrix in R, click here  Download herefor the worksheet in Matrix.
Plus a more detail on what is inverse Matrix, click here  Download here.  Download .This reference was created by Engineering Mathematics first aid kit published by Pearson Education.  
The R code for inverse Matrix: solve(A). This code is the Inverse of A where A is a square matrix. For complete list of Matrix Algebra in R, visit  Dr. Kabacoff, Quick-R at https://www.statmethods.net/advstats/matrix.html (Links to an external site.)

Your Assignment:
Find the value of inverse of a matrix, determinant of a matrix by using the following values:
A=matrix(1:100, nrow=10)
B=matrix(1:1000, nrow=10)
Post your result and procedure you took on your blog.
A good start will be:
>A <- matrix(1:100, nrow=10)  
>B <- matrix(1:1000, nrow=10)


Reading 

Norman Matloff, The Art of R programming pp. 189-205.



```{r Data, echo=TRUE}
A <- matrix(1:100, nrow=10)  
B <- matrix(1:1000, nrow=10)

str(A)
str(B)

# solve(A) creates an error: Lapack routine dgesv: system is exactly singular: U[6,6] = 0
# solve(B) creates a different error: 'a' (10 x 100) must be square
# matrix B is not square, so this does not work.
# solve(A,B) this also gives us an error: Lapack routine dgesv: system is exactly singular: U[6,6] = 0

det(A)

# because the determinant of matrix A is 0, there is no inverse. 

```

