---
title: "Module 6"
author: "Patricia McGee"
date: "2/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment Instructions

Answer the following questions and post your answer on your blog:
1. Consider A=matrix(c(2,0,1,3), ncol=2) and B=matrix(c(5,2,4,-1), ncol=2).
a) Find A + B
b) Find A - B

2. Using the diag() function to build a matrix of size 4 with the following values in the diagonal 4,1,2,3.

3. Generate the following matrix:

## [,1] [,2] [,3] [,4] [,5]
## [1,] 3 1 1 1 1
## [2,] 2 3 0 0 0
## [3,] 2 0 3 0 0
## [4,] 2 0 0 3 0
## [5,] 2 0 0 0 3
Hint: You can use the command diag() to build it.

Reading:
Norman, M. (2011) The Art of R Programming. Chapters 9-10 pp. 207-231.
Wickham, H. (2015) R Packages, organize, test, document and share your code Chapters 2-3. Special attention to Top Level Code - pp 27-31

## Question 1

First, we'll look at question 1 and create the matrices as specified and print them out.

```{r Question1, echo=TRUE}
A <- matrix(c(2,0,1,3), ncol = 2)
B <- matrix(c(5,2,4,-1), ncol = 2)

A
B

# part a)
A+B

#part b)
A-B

```

## Question 2

For the second question, we explore the diag() function and use it to create a matrix.

```{r Question2, echo=TRUE}
?diag
diag(c(4,1,2,3))

```

## Question 3

For the third question, we create the matrix as specified.

```{r Question3, echo=TRUE}
# First we create a matrix with 3s in the diagonals
M <- diag(3,nrow = 5,ncol = 5)
M
# Then we change the first column from rows 2 through 5 to 2s
M[2:5,1] <- 2
M
# Then we change the first row from columns 2 through 5 to 1s
M[1,2:5] <- 1
M


```

